powerboats with `hyper2`

### 2025-03-05 inst/powerboat.Rmd
bugfixes

```{r readpowerboattable}
powerboat_table <- read.table("powerboat.txt",header=TRUE)
```

@@

```{r}
powerboat_table[powerboat_table==0] <- "DNS"
powerboat_table[20:21,8] <- 0  # above does not apply to points
powerboat_table
```

@@

```{r,definsupportb,cache=TRUE}
powerboat <- ordertable2supp(powerboat_table[,1:7])
head(powerboat)
(powerboat_maxp <- maxp(powerboat))
pie(powerboat_maxp)
par(pty="s")
points <- as.numeric(powerboat_table[,8])
names(points) <- rownames(powerboat_table)
points
points <- points[order(names(points))]
points
plot(powerboat_maxp,points*max(powerboat_maxp)/max(points),xlab="likelihood",ylab="points",pch=16)
abline(0,1)
```

>>>>

```{r readpowerboattable}
jj <- read.table("powerboat.txt",header=TRUE)
```

@@

```{r dotable}
powerboat_table <- ordertable(jj[,1:7])
powerboat_table[powerboat_table==0] <- "DNS"
powerboat_table
```

```{r dopoints}
points <- jj[,8]
names(points) <- rownames(powerboat_table)
points <- points[order(names(points))]
points
```

@@

```{r,definsupportb,cache=TRUE}
powerboat <- suppfun(powerboat_table)
(powerboat_maxp <- maxp(powerboat))
```

```{r makeplots}
pie(powerboat_maxp)
par(pty="s")
plot(powerboat_maxp,points/sum(points),xlab="likelihood",ylab="points",pch=16)
abline(0,1)
```
